Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2024-06-10 analysis/Stud1_a.qmd
Updated qmd and docx with total demographics

@@

ggsave("figures/Figure1.png", p1, width=10, height=10, dpi=200, bg="white")
p1
```

>>>>

```{r}

desc <- function(df){
  summary <- df |> summarise(
      n = n(),
      mean = mean(Age, na.rm = TRUE),
      sd = sd(Age, na.rm = TRUE),
      min = min(Age, na.rm = TRUE),
      max = max(Age, na.rm = TRUE),
      female = sum(Gender == "Female", na.rm = TRUE)
    )
    return(summary)
}

desc_df1a <- desc(df1a)
desc_df1b <- desc(df1b)
desc_df2 <- desc(df2)
desc_df3 <- desc(df3)
#desc_df4 <- desc(df4)
#desc_df5 <- desc(df5)
desc_df6 <- desc(df6)
desc_df7a <- desc(df7a)
desc_df7b <- desc(df7b)
desc_df7c <- desc(df7c)
desc_df8a <- desc(df8a)
desc_df8b <- desc(df8b)
desc_df9 <- desc(df9)
desc_df10a <- desc(df10a)
desc_df10b <- desc(df10b)

desc_total <- rbind(desc_df1a, desc_df1b, desc_df2, desc_df3, desc_df6, desc_df7a, desc_df7b, desc_df7c, desc_df8a, desc_df8b, desc_df9, desc_df10a, desc_df10b)

## calculate weighted mean

total_mean = sum(desc_total$mean * desc_total$n) / sum(desc_total$n)
total_sd = sum(desc_total$sd * desc_total$n) / sum(desc_total$n)
perce_female = sum(desc_total$female)/sum(desc_total$n) *100

@@

ggsave("figures/Figure1.png", p1, width=10, height=10, dpi=200, bg="white")
p1

### 2024-06-10 paper/1_Initial/manuscript.qmd
Updated qmd and docx with total demographics

| Samples                  |          | Sample Size | Mean age | SD      | Range   | Female % | Available at           |
|---------|---------|---------|---------|---------|---------|---------|---------|
| Murphy et al., (2020)    |          |             |          |         |         |          |                        |
|                          | Sample 1 | 451         | 25.8     | 8.4     | 18-69   | 69.4%    |                        |
|                          | Sample 2 | 375         | 35.3     | 16.9    | 18-91   | 70.1%    | <https://osf.io/3m5nh> |
| Gaggero et al., (2021)   |          | 814         | 24.9     | 5.3     | 18-58   | 60.3%    | <https://osf.io/5x9sg> |
| Campos et al., (2022)    |          | 515         | 30.7     | 10.5    | 18-72   | 59.6%    | <https://osf.io/j6ef3> |
| Todd et al., (2022)      |          | 802         | 36.58\*  | 12.41\* | 18-92\* | NA       | <https://osf.io/ms354> |
| Arslanova et al., (2022) |          | 96          | 28.78    | 27.5    | 18-73   | 46.8%    | <https://osf.io/mp3cy> |
| Brand et al., (2022)     |          | 619         | 43.9     | 14.5    | 18-78   | 78.7%    | <https://osf.io/xwz6g> |
| Brand et al., (2023)     |          |             |          |         |         |          |                        |
|                          | Sample 1 | 522         | 23.4     | 6.7     | 18-79   | 79.5%    |                        |
|                          | Sample 2 | 1993        | 32.0     | 12.6    | 16-81   | 77.7%    | <https://osf.io/3f2h6> |
|                          | Sample 3 | 802         | 27.3     | 9.3     | 18-72   | 68.9%    |                        |
| Lin et al., (2023)       |          |             |          |         |         |          |                        |
|                          | Sample 1 | 1166        | 32.5     | 8.4     | 16-60   | 57.0%    |                        |
|                          | Sample 2 | 500         | 37.4     | 7.4     | 20-60   | 56.2%    | <https://osf.io/3eztd> |
| VonMohr et al., (2023)   |          | 21843       | 56.5     | 14.4    | 18-93   | 73.2%    | <https://osf.io/7p9u5> |
| Makowski et al., (2023a) |          | 485         | 30.1     | 10.1    | 18-73   | 50.3%    | In preparation\*\*    |
| Makowski et al., (2023b) |          | 251         | 37.5     | 13.2    | 17-76   | 53.0%    | In preparation\*\*    |

**TODO: add row for Total N, average age etc.**
**TODO: add language also, as well as maybe something like "difference" from the original validation (which could acctually be language, and for our the type of scale / less items)**
**TODO: add links to GH for our studies**

The analysed sample contains 31,317 participants, of which xxx are females.

>>>>

| Samples                  |          | Language of Items|  Sample Size | Mean age | SD      | Range   | Female % | Available at           |
|---------|---------|---------|---------|---------|---------|---------|---------|---------|
| Murphy et al., (2020)    |          |             |          |         |         |          |                        |
|                          | Sample 1 | English     |451         | 25.8     | 8.4     | 18-69   | 69.4%    |                        |
|                          | Sample 2 | English     | 375         | 35.3     | 16.9    | 18-91   | 70.1%    | <https://osf.io/3m5nh> |
| Gaggero et al., (2021)   |          | English and Italian   | 814         | 24.9     | 5.3     | 18-58   | 60.3%    | <https://osf.io/5x9sg> |
| Campos et al., (2022)    |          | Portuguese  | 515         | 30.7     | 10.5    | 18-72   | 59.6%    | <https://osf.io/j6ef3> |
| Todd et al., (2022)      |          | English     | 802         | 36.58\*  | 12.41\* | 18-92\* | NA       | <https://osf.io/ms354> |
| Arslanova et al., (2022) |          | English     | 96          | 28.78    | 27.5    | 18-73   | 46.8%    | <https://osf.io/mp3cy> |
| Brand et al., (2022)     |          | German      | 619         | 43.9     | 14.5    | 18-78   | 78.7%    | <https://osf.io/xwz6g> |
| Brand et al., (2023)     |          |             |             |          |         |         |          |                        |
|                          | Sample 1 | German      | 522         | 23.4     | 6.7     | 18-79   | 79.5%    |                        |
|                          | Sample 2 | German      |1993        | 32.0     | 12.6    | 16-81   | 77.7%    | <https://osf.io/3f2h6> |
|                          | Sample 3 | German      | 802         | 27.3     | 9.3     | 18-72   | 68.9%    |                        |
| Lin et al., (2023)       |          |             |             |          |         |         |          |                        |
|                          | Sample 1 | Chinese     | 1166        | 32.5     | 8.4     | 16-60   | 57.0%    |                        |
|                          | Sample 2 | Chinese     | 500         | 37.4     | 7.4     | 20-60   | 56.2%    | <https://osf.io/3eztd> |
| VonMohr et al., (2023)   |          | English     | 21843       | 56.5     | 14.4    | 18-93   | 73.2%    | <https://osf.io/7p9u5> |
| Makowski et al., (2023a) |          | English     | 485         | 30.1     | 10.1    | 18-73   | 50.3%    | In preparation \*\*    |
| Makowski et al., (2023b) |          | English     |251         | 37.5     | 13.2    | 17-76   | 53.0%    | In preparation \*\*    |
| Total                    |          |             |31317       | 49.5     | 13.2    | 17 - 93 | 71.5%    | |
**Note**. \* Numbers were sourced from the original paper rather than independently calculated. \*\* Data for Makowski et al., 2023a: <https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv> and Makowski et al., 2013b: <https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv>
<!-- **TODO: add row for Total N, average age etc.** -->
**TODO: add language also, as well as maybe something like "difference" from the original validation (which could actually be language, and for our the type of scale / less items)**
**TODO: add links to GH for our studies**

The analysed sample contains 31,317 participants, of which 71.5% are females.
